\documentclass[11pt,a4paper]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[left=0.75in, right=0.75in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% --- Formatting ---
\pagestyle{empty} % Remove page numbers
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

% Section line styling
\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}

\begin{document}

% --- Header ---
\begin{center}
    {\Huge \textbf{Salvador de Sousa Carvalho}} \\
    \vspace{2pt}
    {\footnotesize (last updated: 2026/03/14)}
\end{center}

\vspace{0.2cm}

\noindent
\begin{minipage}[t]{0.5\textwidth}
    Lisboa, Portugal \\
    (+351) 915 518 741 \\
    \href{mailto:salvadorcarvalho2005@gmail.com}{salvadorcarvalho2005@gmail.com}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
    \raggedleft
    \href{https://salvadorcarvalho.pt}{salvadorcarvalho.pt} \\
    \href{https://github.com/CARVALHOCENT}{github.com/SalvadorCarvalho} \\
    \href{https://www.linkedin.com/in/salvadordesousacarvalho/}{https://www.linkedin.com/in/SalvadorCarvalho}
\end{minipage}

% --- About Section ---
\section*{About}

I am a 3rd-year Electrical and Computer Engineering student at \textbf{Instituto Superior Técnico} focused on developing my skills both on hardware and software. My entire life as been marked for a long standing curiosity for knowing how things work, it all began with simple sets of Lego Technic and evolved to more technical topics like \textbf{Robotics, IoT, and Home Automation}. 

With a \textbf{Cambridge C1 Advanced} certification and currently learning German, I am eager to keep learning and pushing myself into new challenges and to apply what I learn to new projects.


% --- Experience Section ---
\section*{Experience}

\noindent \textbf{Formula Student Lisboa}, Lisbon, Portugal \hfill Jan 2025 -- Aug 2025 \\
\textit{Trainee}, Electronics and Software Department
\begin{itemize}[leftmargin=15pt, label={$\bullet$}]
    \item Designed and developed electronic schematics and PCB layouts for the vehicle's braking system sensors using \textbf{Altium Designer}.
    \item Programmed microcontrollers in \textbf{C and C++} to process sensor data and implement real-time control logic for the braking system.
    \item Performed high-precision \textbf{soldering} and hardware assembly, ensuring the reliability of electronic components in high-performance environments.
    \item Collaborated in team communication and technical presentations, effectively reporting progress and system design specifications.
\end{itemize}


% --- Education Section ---
\section*{Education}

% Instituto Superior Técnico
\noindent \textbf{Instituto Superior Técnico}, Lisbon, Portugal \hfill Sep 2023 -- Present \\
\textit{Bachelor of Science in Electrical and Computer Engineering} 

\vspace{8pt}

% Colégio de São Miguel - Secundário
\noindent \textbf{Colégio de São Miguel}, Fátima, Portugal \hfill Sep 2020 -- Jun 2023 \\
\textit{Secondary Education, Ciências e Tecnologias} \hfill \textbf{GPA: 17.2/20} \\
\textit{\small National Mathematics Exam: 18.1/20}

% --- Projects Section ---
\section*{Projects}

\noindent \textbf{Forest Fire Detection System (PIC)} \hfill In Development
\begin{itemize}[leftmargin=15pt, label={$\bullet$}, noitemsep, topsep=2pt]
    \item Developed an integrated monitoring system for early fire detection using a \textbf{YOLO-based} AI model for real-time smoke identification via camera modules.
    \item Integrated environmental sensors with \textbf{Meshtastic (LoRa)} to enable long-range, off-grid communication in remote forest areas.
    \item Built a custom \textbf{unified dashboard} to aggregate sensor telemetry and AI visual alerts into a single, real-time control interface.
\end{itemize}

\noindent \textbf{Distributed Resource Sharing System (RC)} (\href{https://github.com/CARVALHOCENT/Computer-Networks-and-the-Internet }{GitHub})\hfill In Development 
\begin{itemize}[leftmargin=15pt, label={$\bullet$}, noitemsep, topsep=2pt]
    \item Engineered a distributed application in \textbf{C} using a client-server and peer-to-peer architecture.
    \item Implemented reliable data transfer and discovery protocols using \textbf{TCP and UDP socket programming}.
    \item Developed a concurrent server capable of handling multiple simultaneous requests with robust error handling.
\end{itemize}

\noindent \textbf{Image Watermark \& PDF Processor}(\href{https://github.com/CARVALHOCENT/WatermarkApp }{GitHub})\hfill 2025 
\begin{itemize}[leftmargin=15pt, label={$\bullet$}, noitemsep, topsep=2pt]
    \item Developed a \textbf{React} web application for processing JPEG images with custom watermarks.
    \item Integrated \textbf{Canvas API} for dynamic image manipulation and \textbf{jsPDF} for secure PDF generation.
    \item Implemented 100\% client-side processing to ensure data privacy and responsive UI with \textbf{Tailwind CSS}.
\end{itemize}

\noindent \textbf{Algorithms and Data Structures Projects} (\href{https://github.com/CARVALHOCENT/AED-Projetos}{GitHub}) \hfill 2025 
\begin{itemize}[leftmargin=15pt, label={$\bullet$}]
    \item Developed a series of applications in \textbf{C} focused on algorithmic efficiency and memory management. Implemented data structures including \textbf{Min-Heaps, Linked Lists, and Hash Tables}, and applied graph algorithms such as \textbf{Dijkstra} for shortest-path problems. Focused on optimizing time and space complexity ($O$-notation) to handle large datasets.
\end{itemize}

\noindent \textbf{Image Watermark \& PDF Processor}(\href{https://github.com/CARVALHOCENT/WatermarkApp }{GitHub})\hfill 2025 
\begin{itemize}[leftmargin=15pt, label={$\bullet$}, noitemsep, topsep=2pt]
    \item Developed a \textbf{React} web application for processing JPEG images with custom watermarks.
    \item Integrated \textbf{Canvas API} for dynamic image manipulation and \textbf{jsPDF} for secure PDF generation.
    \item Implemented 100\% client-side processing to ensure data privacy and responsive UI with \textbf{Tailwind CSS}.
\end{itemize}

\noindent \textbf{CS2 \& Faceit Discord Bot} (\href{https://github.com/CARVALHOCENT/Discord-Bot-CS2}{GitHub}) \hfill 2025 
\begin{itemize}[leftmargin=15pt, label={$\bullet$}]
    \item Developed a custom Discord bot using \textbf{discord.py} and \textbf{aiohttp} to integrate Faceit API data and live CS2 server status via the A2S protocol. Implemented real-time Elo tracking, match statistics retrieval, and an interactive server browser menu, alongside a voice-system module utilizing \textbf{FFmpeg and PyNaCl} for custom audio playback.
\end{itemize}

\vspace{6pt}

\noindent \textbf{5-DOF Robotic Arm} (\href{https://github.com/CARVALHOCENT/RobotArm}{GitHub}, \href{https://www.youtube.com/watch?v=mb50L6tp-c0}{Video}, \href{https://github.com/CARVALHOCENT/RobotArm/blob/main/Projeto_Fisica_e_API.pdf}{Report}) \hfill 2023 
\begin{itemize}[leftmargin=15pt, label={$\bullet$}]
    \item Developed a 5-DOF robotic arm control system using Arduino and C++, featuring a Serial interface for real-time joint manipulation and user interaction. Implemented input validation and safety constraints for servo positioning to ensure smooth kinematic movement and hardware longevity. Documented the complete electronic circuit design and firmware architecture in a detailed technical report.
\end{itemize}

% --- Honors & Awards Section ---
\section*{Honors \& Awards}

\noindent \textbf{Merit Board}, Colégio do Sagrado Coração de Maria \hfill 2017/18, 2018/19, 2019/20 \\
\noindent \textbf{Honor Board}, Colégio do Sagrado Coração de Maria \hfill 2017/18, 2018/19, 2019/20 \\
\noindent \textbf{Merit Board}, EB1 Reguengo do Fetal \hfill 2013/14 \\

% --- Certificates Section ---
\section*{Certificates}

\noindent \textbf{Cambridge Advanced English}, Cambridge English \hfill Aug 2023 \\
\noindent \textbf{Cambridge First Certificate in English}, Cambridge English \hfill Jul 2022

% --- Skills and Interests Section ---
\section*{Skills and Interests}

\begin{itemize}[leftmargin=1.5em, labelsep=0.5em]
    \item[] Hard skills:
    \begin{itemize}[label=\tiny$\bullet$, leftmargin=1.5em, noitemsep, topsep=2pt]
        \item Programming:C/C++, Python, MATLAB, Simulink, Fusion360
        \item Tools \& Frameworks: Git, Docker, Linux, LTSPICE
    \end{itemize}
    \vspace{4pt}
    \item[] Soft skills: Analytical \& Creative Thinking, Team Collaboration, Adaptability \& Communication
    \item[] Language skills: Portuguese (native), English (C1), German (A1)
\end{itemize}

\end{document}